### 2013-09-17 main.tex
work on conclusions

There are several directions for future research that we think would be interesting to pursue as an extention
of the presented results: 
\paragraph[Inference Machines]
Recently \citet{stoyanov2011empirical} started a new trend in structured
prediction, which is sometimes called ``inference machines''. The basic
principle is simple: view the process of prediction with a given inference
procedure as a prediction method and optimize parameters of this method using
empirical risk minimization.  The work of \citet{stoyanov2011empirical}, used
loopy belief propagation as their inference algorithm and the optimization is
carried out simply using gradient descent on the non-convex but differentiable
loss function.  Other recent work in this direction includes
\citet{krahenbuhlparameter}, who used mean-field inference in a fully connected
conditional random field and \citet{jancsarylearning}, who used closed form
inference in a Gaussian CRF\@.
While these algorithms show great promise, their relation to the traditional
approach of structured prediction used in this work is mostly unclear. In particular,
if exact traditional learning is possible in a model, it is unclear how much
can be gained by direct empirical risk minimization.
Little empirical comparision was performed, and we are not aware of theoretical
work in this direction, leaving much room for future investigation of this
direction.
\paragraph[Non-Linear Models]
In this work, we only considered models that are linear in the input features--though
features are highly non-linear in the original input pixels.
Kernelization of structural support vector machines is trivial in theory, but
had only limited success in the context of CRFs for image
segmentation~\citep{lucchi2012structured}.
Other

>>>>

There are several directions for future research that we think would be interesting to pursue as an extention
of the presented results: 
\paragraph[Inference Machines]
Recently \citet{stoyanov2011empirical} started a new trend in structured
prediction, which is sometimes called ``inference machines''. The basic
principle is simple: view the process of prediction with a given inference
procedure as a prediction method and optimize parameters of this method using
empirical risk minimization.  The work of \citet{stoyanov2011empirical}, used
loopy belief propagation as their inference algorithm and the optimization is
carried out simply using gradient descent on the non-convex but differentiable
loss function.  Other recent work in this direction includes
\citet{krahenbuhlparameter}, who used mean-field inference in a fully connected
conditional random field and \citet{jancsarylearning}, who used closed form
inference in a Gaussian CRF\@.
While these algorithms show great promise, their relation to the traditional
approach of structured prediction used in this work is mostly unclear. In particular,
if exact traditional learning is possible in a model, it is unclear how much
can be gained by direct empirical risk minimization.
Little empirical comparision was performed, and we are not aware of theoretical
work in this direction, leaving much room for future investigation of this
direction.
\paragraph[Non-Linear Models]
In this work, we only considered models that are linear in the input features--though
features are highly non-linear in the original input pixels.
Kernelization of structural support vector machines is trivial in theory, but
had only limited success in the context of CRFs for image
segmentation~\citep{lucchi2012structured}.
Two major alternatives for non-linear CRFs were proposed in the literature,
conditional neural fields~\citep{peng2009conditional} based on neural networks,
and decision tree fields~\citep{nowozin2011decision}, based on decision trees.
Conditional neural fields have only applied to sequence classification so far,
and extending them to our setting of semantic image segmentation would be very
interesting. Decision tree fields~(DTFs) on the other hand have been applied to loopy
graphs for image processing, but not for higher level tasks such as semantic
segmentation. If it is possible to include context in a meaningful way, it
might be possible to solve even object-centric tasks such as object class
segmentation with DTFs.
